Les besoins en éducation pour les pratiques opensource

### 2022-02-02 main.tex
start customizing the template

\documentclass[
    a4paper,
    twoside=true,
    open=true,
    fontsize=12pt,
]{report}

\usepackage[french,english]{babel}
\usepackage{graphicx}
\graphicspath{{images/}}

\title{
    {Mémoire de recherche, M2 Science de l'Éducation, parcours SYNVA}\\
    {\large UNISTRA}\\
    {\includegraphics[width=0.5\textwidth]{Signature_Universite_Strasbourg_Unistra2_Transparent}}
}
\author{Paul Hervot}
\date{\today}

@@

\maketitle

>>>>

% Load the kaobook class
\documentclass[
	fontsize=10pt, % Base font size
	twoside=true, % Use different layouts for even and odd pages (in particular, if twoside=true, the margin column will be always on the outside)
	open=any, % If twoside=true, uncomment this to force new chapters to start on any page, not only on right (odd) pages
	secnumdepth=1, % How deep to number headings. Defaults to 1 (sections)
]{kaobook}

% Choose the language
\usepackage[main=french,english]{babel} % Load characters and hyphenation
\usepackage{csquotes}

% Load packages for testing
\usepackage{blindtext}
%\usepackage{showframe} % Uncomment to show boxes around the text area, margin, header and footer
%\usepackage{showlabels} % Uncomment to output the content of \label commands to the document where they are used

% Load the bibliography package
\usepackage{kaobiblio}
\addbibresource{references.bib} % Bibliography file

% Load mathematical packages for theorems and related environments
\usepackage{kaotheorems}

% Load the package for hyperreferences
\usepackage{kaorefs}

\graphicspath{{images/}{./}} % Paths where images are looked for

\makeindex[columns=3, title=Alphabetical Index, intoc] % Make LaTeX produce the files required to compile the index

@@

%----------------------------------------------------------------------------------------
%	BOOK INFORMATION
%----------------------------------------------------------------------------------------

\titlehead{}
\title{Les besoins en éducation pour les pratiques opensource}
\subtitle{Mémoire de M2 Sciences de l'Éducation, parcours SYNVA}
\author[PH]{Paul Hervot}
\date{\today}
\publishers{Université de Strasbourg} % TODO: is it really the publisher?

%----------------------------------------------------------------------------------------

\frontmatter % Denotes the start of the pre-document content, uses roman numerals

%----------------------------------------------------------------------------------------
%	COPYRIGHT PAGE
%----------------------------------------------------------------------------------------

\makeatletter
\uppertitleback{\@titlehead} % Header

\lowertitleback{
    \textbf{No copyright} \\
    \ccby\ Ce mémoire est mis à disposition selon les termes de la
    \href{https://creativecommons.org/licenses/by/3.0/fr/}{Licence Creative
    Commons Attribution}.

    \medskip

    \textbf{Colophon} \\
    Ce document a été composé avec l'aide de
    \href{https://sourceforge.net/projects/koma-script/}{\KOMAScript} et
    \href{https://www.latex-project.org/}{\LaTeX} en utilisant la classe
    \href{https://github.com/fmarotta/kaobook/}{kaobook}.

    \medskip

    \textbf{Publisher} \\
    Première publication le TODO \@publishers % TODO
}
\makeatother

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedication{
    Insérer ici une citation engageante.\\
    \flushright -- Personne toute autant engageante
    % TODO
}

%----------------------------------------------------------------------------------------
%	OUTPUT TITLE PAGE AND PREVIOUS
%----------------------------------------------------------------------------------------

% Note that \maketitle outputs the pages before here
\maketitle

%----------------------------------------------------------------------------------------
%	PREFACE
%----------------------------------------------------------------------------------------

\chapter*{Préface}

\Blindtext

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS & LIST OF FIGURES/TABLES
%----------------------------------------------------------------------------------------

\begingroup % Local scope for the following commands

% Define the style for the TOC, LOF, and LOT
%\setstretch{1} % Uncomment to modify line spacing in the ToC
%\hypersetup{linkcolor=blue} % Uncomment to set the colour of links in the ToC
\setlength{\textheight}{230\vscale} % Manually adjust the height of the ToC pages

% Turn on compatibility mode for the etoc package
\etocstandarddisplaystyle % "toc display" as if etoc was not loaded
\etocstandardlines % "toc lines as if etoc was not loaded

\tableofcontents % Output the table of contents

\listoffigures % Output the list of figures

% Comment both of the following lines to have the LOF and the LOT on different pages
\let\cleardoublepage\bigskip
\let\clearpage\bigskip

\listoftables % Output the list of tables

\endgroup

%----------------------------------------------------------------------------------------
%	MAIN BODY
%----------------------------------------------------------------------------------------

\mainmatter % Denotes the start of the main document content, resets page numbering and uses arabic numbers
\setchapterstyle{kao} % Choose the default chapter heading style

\chapter{Premier chapitre}

\Blinddocument

\pagelayout{wide} % No margins
\addpart{Titre de la partie}
\pagelayout{margin} % Restore margins

\chapter{Deuxième chapitre}

\Blinddocument

\appendix % From here onwards, chapters are numbered with letters, as is the appendix convention

\pagelayout{wide} % No margins
\addpart{Appendices}
\pagelayout{margin} % Restore margins

\chapter{Some more blindtext}

\Blinddocument

%----------------------------------------------------------------------------------------

\backmatter % Denotes the end of the main document content
\setchapterstyle{plain} % Output plain chapters from this point onwards

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

% The bibliography needs to be compiled with biber using your LaTeX editor, or on the command line with 'biber main' from the template directory

\defbibnote{bibnote}{Here are the references in citation order.\par\bigskip} % Prepend this text to the bibliography
\printbibliography[heading=bibintoc, title=Bibliography, prenote=bibnote] % Add the bibliography heading to the ToC, set the title of the bibliography and output the bibliography note

%----------------------------------------------------------------------------------------
%	INDEX
%----------------------------------------------------------------------------------------

% The index needs to be compiled on the command line with 'makeindex main' from the template directory

\printindex % Output the index
